Comparison of long and short amplicon metabarcoding for determination of fungal species diversity and spatial turnover in an ectomycorrhizal West African woodland

### 2019-08-12 writing/MSA2019_presentation.Rnw
add logo, comment out unneeded slides

\title{Comparison of long and short amplicon metabarcoding for determination of fungal species diversity and spatial turnover in an ectomycorrhizal West African woodland}
\author{\mbox{\textbf{Brendan Furneaux}\inst{1}} \and \mbox{Mohammad Bahram\inst{2}} \and \mbox{Nourou Yorou\inst{3}} \and \mbox{Anna Rosling\inst{1}} \and \mbox{Martin Ryberg\inst{1}}}
\institute{\inst{1}Uppsala University \and \inst{2}Swedish University of Agricultural Sciences \and \inst{3}University of Parakou}
\date{13 August, 2019}

@@

\begin{frame}{Sequencing}
  \framesubtitle{Which platform?}
  \begincols
  \begincol{0.5\linewidth}
    \begin{block}{IonTorrent}
      \begin{itemize}
        \tightlist
        \item Low cost per bp.
        \item Smaller minimum job than Illumina.
        \item Needs less DNA than PacBio.
        \item Bias against amplicons greater than 400 bp.
         \item Cannot sequence long ITS+LSU amplicon.
       \end{itemize}
     \end{block}
  \endcol
  \begincol{0.5\linewidth}
     \begin{block}{PacBio}
        \begin{itemize}
          \tightlist
          \item Higher cost per bp $\implies$ fewer samples or less sequencing depth for same budget.
          \item Requires more DNA.
          \item Good accuracy requires multiple circular reads.
        \end{itemize}
      \end{block}
  \endcol
  \endcols
  \centering

\end{frame}

\begin{frame}{Sequencing}
  \begin{block}{The plan}
  Three sequencing runs:
  \begin{itemize}
    \item Ion Proton S5, short amplicon
    \begin{itemize}
      \item Pool all samples on one chip
    \end{itemize}
    \item PacBio RSII, short amplicon
    \begin{itemize}
      \item Same amplicon library as IonTorrent.
      \item Two sequencing libraries, two SMRT cells per library.
    \end{itemize}
    \item PacBio RSII, long amplicon
    \begin{itemize}
      \item Two sequencing libraries, four SMRT cells per library.
    \end{itemize}
  \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Sequencing}
  \begin{block}{What happened}
  Three sequencing runs:
  \begin{itemize}
    \item \sout{IonTorrent, short amplicon}
    \begin{itemize}
      \item Accidentally used primers with IonTorrent adapters built in.
      \item Lost some of the multiplexing barcodes.
      \item Can't demultiplex the samples --- can only look at pool of all reads.
    \end{itemize}
    \item PacBio, short amplicon
    \begin{itemize}
      \item OK
    \end{itemize}
    \item PacBio, long amplicon
    \begin{itemize}
      \item OK
    \end{itemize}
  \end{itemize}
  \end{block}
\end{frame}

@@

<<errorrate, fig.width = 12>>=
ggplot(reads_subset, aes(x = erate,
                  linetype = Dataset,
                  group = paste(Dataset, Region),
                  color = Region)) +
  geom_line(aes(y = 1 - ..y..), stat = "ecdf") +
  scale_x_continuous(name = "Expected number of errors per base",
                     trans = reverselog_trans(10),
                     limits = c(NA, 1e-5),
                     oob = squish) +
  scale_y_continuous(name = "Fraction passing") +
  scale_color_viridis_d(option = "C") +
  scale_linetype_discrete()
@
\end{frame}

@@

<<totalerror, fig.width = 12>>=
ggplot(reads_subset, aes(x = eexp,
                  linetype = Dataset,
                  group = paste(Dataset, Region),
                  color = Region)) +
  geom_line(aes(y = 1 - ..y..), stat = "ecdf") +
  scale_x_continuous(name = "Expected number of errors",
                     trans = reverselog_trans(10),
                     limits = c(NA, 0.1),
                     oob = squish) +
  scale_y_continuous(name = "Fraction passing") +
  scale_color_viridis_d(option = "C") +
  scale_linetype_discrete()
@
\end{frame}

>>>>

\title{Comparison of long and short amplicon metabarcoding for determination of fungal species diversity and spatial turnover in an ectomycorrhizal West African woodland}
\author{\mbox{\textbf{Brendan Furneaux}\inst{1}} \and \mbox{Mohammad Bahram\inst{2}} \and \mbox{Nourou Yorou\inst{3}} \and \mbox{Anna Rosling\inst{1}} \and \mbox{Martin Ryberg\inst{1}}}
\institute{\inst{1}Uppsala University \and \inst{2}Swedish University of Agricultural Sciences \and \inst{3}University of Parakou}
\date{13 August, 2019}
\logo{\includegraphics[width=2.5cm]{Uppsala_University_logo}}

@@

% \begin{frame}{Sequencing}
%   \framesubtitle{Which platform?}
%   \begincols
%   \begincol{0.5\linewidth}
%     \begin{block}{IonTorrent}
%       \begin{itemize}
%         \tightlist
%         \item Low cost per bp.
%         \item Smaller minimum job than Illumina.
%         \item Needs less DNA than PacBio.
%         \item Bias against amplicons greater than 400 bp.
%          \item Cannot sequence long ITS+LSU amplicon.
%        \end{itemize}
%      \end{block}
%   \endcol
%   \begincol{0.5\linewidth}
%      \begin{block}{PacBio}
%         \begin{itemize}
%           \tightlist
%           \item Higher cost per bp $\implies$ fewer samples or less sequencing depth for same budget.
%           \item Requires more DNA.
%           \item Good accuracy requires multiple circular reads.
%         \end{itemize}
%       \end{block}
%   \endcol
%   \endcols
%   \centering
% 
% \end{frame}
% 
% \begin{frame}{Sequencing}
%   \begin{block}{The plan}
%   Three sequencing runs:
%   \begin{itemize}
%     \item Ion Proton S5, short amplicon
%     \begin{itemize}
%       \item Pool all samples on one chip
%     \end{itemize}
%     \item PacBio RSII, short amplicon
%     \begin{itemize}
%       \item Same amplicon library as IonTorrent.
%       \item Two sequencing libraries, two SMRT cells per library.
%     \end{itemize}
%     \item PacBio RSII, long amplicon
%     \begin{itemize}
%       \item Two sequencing libraries, four SMRT cells per library.
%     \end{itemize}
%   \end{itemize}
%   \end{block}
% \end{frame}
% 
% \begin{frame}{Sequencing}
%   \begin{block}{What happened}
%   Three sequencing runs:
%   \begin{itemize}
%     \item \sout{IonTorrent, short amplicon}
%     \begin{itemize}
%       \item Accidentally used primers with IonTorrent adapters built in.
%       \item Lost some of the multiplexing barcodes.
%       \item Can't demultiplex the samples --- can only look at pool of all reads.
%     \end{itemize}
%     \item PacBio, short amplicon
%     \begin{itemize}
%       \item OK
%     \end{itemize}
%     \item PacBio, long amplicon
%     \begin{itemize}
%       \item OK
%     \end{itemize}
%   \end{itemize}
%   \end{block}
% \end{frame}

@@

% <<errorrate, fig.width = 12>>=
% ggplot(reads_subset, aes(x = erate,
%                   linetype = Dataset,
%                   group = paste(Dataset, Region),
%                   color = Region)) +
%   geom_line(aes(y = 1 - ..y..), stat = "ecdf") +
%   scale_x_continuous(name = "Expected number of errors per base",
%                      trans = reverselog_trans(10),
%                      limits = c(NA, 1e-5),
%                      oob = squish) +
%   scale_y_continuous(name = "Fraction passing") +
%   scale_color_viridis_d(option = "C") +
%   scale_linetype_discrete()
% @
\end{frame}

@@

% <<totalerror, fig.width = 12>>=
% ggplot(reads_subset, aes(x = eexp,
%                   linetype = Dataset,
%                   group = paste(Dataset, Region),
%                   color = Region)) +
%   geom_line(aes(y = 1 - ..y..), stat = "ecdf") +
%   scale_x_continuous(name = "Expected number of errors",
%                      trans = reverselog_trans(10),
%                      limits = c(NA, 0.1),
%                      oob = squish) +
%   scale_y_continuous(name = "Fraction passing") +
%   scale_color_viridis_d(option = "C") +
%   scale_linetype_discrete()
% @
\end{frame}
